# The Full Pipeline {.unnumbered}  
### [Try It Yourself](http://morpheus.users.weber.edu:8000/)  
## Full App Migration
I have migrated the demo into a much more robust Flask app, and it now supports several more features. 

- Session
    - A user has a session that keeps track of all the submissions (the timestamp, image, code results, etc.)
- Session History
    - This is where the user can view all the information tracked by the current session in a summary screen
    - Includes an easy-to-read PDF export
- Sessions History (history of all sessions)
    - A history of the current and past sessions, so progress isn't accidentally lost
- New Session
    - A user can start a new session anytime they choose
    - Once a session is ended, it is considered "archived" and cannot be changed

User sessions are built using a UUID system, so there is no login/logout or user state. The user's session UUIDs are stored for 30 days in their cookies locally, and the site generates based upon that, using the information stored in the DB (and the images stored on the disk)

## Full Pipeline load testing

I made a `load_test.py` script that allows for testing the full pipeline with concurrent requests.  

I ran 5 consecutive load tests, each with 10 users and a different image each to go through the whole process each time.  

Below are two different figures that I made based on the results of those tests.  

The first shows the increasing wait time for each user, and the second shows the variance accounting for the increasing queue time.  



```{r}
#| label: fig-load-times
#| fig-cap: "Load test completion time by user order, across 5 test runs"
#| code-fold: true

library(ggplot2)

times <- c(16.27, 18.28, 20.65, 22.92, 25.32, 27.47, 29.69, 32.43, 35.17, 37.53,
           17.85, 19.52, 21.31, 22.99, 24.80, 26.73, 28.46, 30.29, 32.15, 34.04,
           12.61, 14.14, 15.71, 17.51, 19.11, 20.73, 22.25, 24.02, 25.47, 27.35,
            9.62, 12.79, 16.02, 19.05, 22.72, 25.45, 28.85, 31.67, 35.50, 38.88,
            4.89,  6.65,  8.44, 10.20, 12.00, 13.78, 15.49, 17.29, 19.03, 20.86)

df <- data.frame(
  time = times,
  run = factor(rep(1:5, each = 10)),
  user_position = rep(1:10, times = 5)
)

ggplot(df, aes(x = user_position, y = time, color = run)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Pipeline Completion Steadily Increases",
       x = "User position (order of finish)",
       y = "Elapsed time since test start (seconds)",
       color = "Run") +
  theme_minimal(base_size = 13)
```

- Completion time increases steadily with each additional consecutive user in every run
    - This is consistent with a single-threaded bottleneck (the local LLM OCR process) queueing requests.

- Run 5 starts fastest and stays lowest throughout, while Runs 1–4 cluster closer together 
    - This matches my manual use of the LLM for OCR, occasionally it gets hung up *or* processes very quickly.
    - This variance has occured with the same image being translated over and over, so I don't believe it likely that it differs entirely based on input.

```{r}
#| label: fig-marginal-delay
#| fig-cap: "Marginal time added per additional consecutive user, by run"
#| code-fold: true
#| message: false

library(dplyr)

deltas <- df %>%
  group_by(run) %>%
  arrange(user_position) %>%
  mutate(delta = time - lag(time)) %>%
  filter(!is.na(delta))

ggplot(deltas, aes(x = user_position, y = delta, color = run)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = 2:10) +
  labs(title = "OCR Bottleneck Adds ~2 Seconds per Additional User",
       x = "Nth consecutive user",
       y = "Added time vs. previous user (seconds)",
       color = "Run") +
  theme_minimal(base_size = 13)
```

- Most runs add a fairly consistent ~1–2 seconds per additional consecutive user
    - gives a reasonable estimate of the actual per-request cost of the local LLM doing OCR under load.

- Run 4 stands out with a higher (~3–3.8s) and less consistent cost, indicating the bottleneck isn't always stable.
	- It may be worth investigating what factors contributed to this inconsistency, and if the LLM can be made to return more quickly and consistently under different parameters

### Overall stats

- Count:          50
- Sum:            1091.95s
- Mean:           21.839s
- Median:         21.085s
- Largest:        38.88s
- Smallest:       4.89s
- Range:          33.99s
- Std. Deviation:	8.18s

**Images used:**

- test-write.jpg
- test-network.jpg
- code-to-text.jpg
- code-to-text-2.jpeg
- code-to-text-3.jpeg

## Load Testing with varied images  
I adjusted the `load_test.py` script to be able to handle different images, and I reran the 10 concurrent users test with 5 different images (each submitted twice by a different "user")  

```{r}
#| label: fig-load-times-varied
#| fig-cap: "Load test completion time by user order, across 5 test runs (5 distinct images, each submitted twice)"
#| code-fold: true

library(ggplot2)

times <- c(4.66, 7.47, 9.29, 15.22, 19.76, 22.12, 23.66, 26.38, 31.22, 34.23,
           4.68, 7.05, 12.55, 13.21, 17.97, 18.96, 25.52, 29.73, 31.56, 34.51,
           12.44, 18.76, 20.29, 26.07, 28.47, 29.01, 34.14, 34.41, 41.84, 43.66,
           8.97, 9.67, 10.69, 17.15, 18.93, 19.95, 21.35, 26.23, 28.95, 34.71,
           12.65, 14.79, 21.21, 22.66, 25.38, 29.98, 32.94, 35.69, 37.63, 39.95)

df_varied <- data.frame(
  time = times,
  run = factor(rep(1:5, each = 10)),
  user_position = rep(1:10, times = 5)
)

ggplot(df_varied, aes(x = user_position, y = time, color = run)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = 1:10) +
  labs(title = "Pipeline Completion Time with Varied Image Content",
       x = "Submission position (order of finish)",
       y = "Elapsed time since test start (seconds)",
       color = "Run") +
  theme_minimal(base_size = 13)
```

- The times are less strictly linear, but still follow a fairly consistent pattern, and are all within an acceptable time frame. 

```{r}
#| label: fig-marginal-delay-varied
#| fig-cap: "Marginal time added per additional consecutive submission, by run (varied images)"
#| code-fold: true
#| message: false

library(dplyr)

deltas_varied <- df_varied %>%
  group_by(run) %>%
  arrange(user_position) %>%
  mutate(delta = time - lag(time)) %>%
  filter(!is.na(delta))

ggplot(deltas_varied, aes(x = user_position, y = delta, color = run)) +
  geom_line(linewidth = 0.8) +
  geom_point(size = 2) +
  scale_x_continuous(breaks = 2:10) +
  labs(title = "OCR Bottleneck Cost with Varied Image Content",
       x = "Nth consecutive submission",
       y = "Added time vs. previous submission (seconds)",
       color = "Run") +
  theme_minimal(base_size = 13)
```

The variance here has a much greater difference from run to run, and also varies much more than the single image tests. This seems to indicate a closer to real-world example of 10 concurrent users.  

The time added per consecutive user is much greater, but still within a very reasonable threshold, and all 50 submissions succeeding without needing to be edited is a great sign for the consistency of the OCR.  


### My Takeaway (after improving the test)

- Less than a third of the submissions take more than 4 seconds to process, a tenth of them more than 6 seconds, none of them more than 7. 
  - The site should be able to handle 10 users submitting at the exact same moment, and if there are less than 20 users actively using the site then load times should remain acceptable. 
  - Above that number, we may begin to run into issues, though this should only happen right before due dates, and if several classes are using the tool. I don't imagine that more than 20 students from a 40 student class would be submitting at the same time if it is used as a homework tool. 

- The primary bottleneck is the OCR, so I could attempt to see if it is possible or better to run multiple instances of the LLMs doing the translation, but I suspect that the performance cost of multiple instances may actually increase load times overall. 